Search, Compress, Compile: Library Learning in Neurally-Guided Bayesian Program Learning

### 2018-07-07 archive.tex
poster acknowledgments

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usepackage{circuitikz}
\usetikzlibrary{fit,bayesnet}
%\usetikzlibrary{arrows.meta}
%\usetikzlibrary{positioning}
%\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration=snake}}
\usepackage{dsfont}
\usepackage{amsmath}

@@

    \node[draw,rounded corners, inner sep = 10] at ([xshift = 4.5cm,yshift = -1cm]) (s){Search};

@@

    \node at (7,-1) (f) {Frontier};
    \draw [->  ] (s.east) -- (f.west);

@@

  \begin{tikzpicture}
    \node at (0,0) (d){DSL};
    \node at ([xshift = 3cm]d.east) (p2){program};
    \node at ([yshift = 1.5cm]p2) (p1){program};
    \node at ([yshift = -1.5cm]p2) (p3){program};

@@

    \node at ([yshift = -0.5cm]p3.south) {\textsc{\textbf{Sleep-R: Experience Replay}}};
  \end{tikzpicture}
  \vspace{2cm}

  \begin{tikzpicture}
    \node at (0,0) (f1){Frontier$_1$};
    \node at ([yshift = -1cm]f1.south) (f2){Frontier$_2$};
    \node at ([yshift = -1cm]f2.south) (ff){$\vdots$};
    \node at ([yshift = -1cm]ff.south) (f3){Frontier$_N$};

@@

    \node[align = right](d) at ([xshift = 1.5cm,yshift = 1cm]c.east) {DSL $\mathcal{D}$};
    \node[align = right](t) at ([xshift = 1.5cm,yshift = -1cm]c.east) {Parameters $\theta$};
    \draw [-> ] (c.east) -- (d.west);
    \draw [-> ] (c.east) -- (t.west);

>>>>

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usepackage{circuitikz}
\usetikzlibrary{fit,bayesnet}
%\usetikzlibrary{arrows.meta}
%\usetikzlibrary{positioning}
%\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{dsfont}
\usepackage{amsmath}

@@

    \node[draw,rounded corners, inner sep = 10] at ([xshift = 4.2cm,yshift = -1cm]) (s){Search};
    \node at ([xshift=-7pt,yshift=5pt]s.north west) {$\mathcal{D}$};

@@

    \node[align=left] at (7,-1) (f) {Frontier\\{\small (set of programs)}};
    \draw [->  ] (s.east) -- (f.west);

@@

@@

    \node at ([yshift = -0.5cm]p3.south) {\textsc{\textbf{Sleep-R: Experience Replay}}};
  \end{tikzpicture}

  \begin{tikzpicture}
    \node[align=center] at (0,0) (d){DSL\\$(\mathcal{D},\theta)$};
    \node at ([xshift = 3cm]d.east) (p2){program};
    \node at ([yshift = 1.5cm]p2) (p1){program};
    \node at ([yshift = -1.5cm]p2) (p3){program};

  \vspace{2cm}

  \begin{tikzpicture}
    \node at (0,0) (f1){Frontier$_1$};
    \node at ([yshift = -1cm]f1.south) (f2){Frontier$_2$};
    \node at ([yshift = -0.7cm]f2.south) (ff){\textbf{$\vdots$}};
    \node at ([yshift = -1.2cm]f2.south) (ff){\textbf{$\vdots$}};
    \node at ([yshift = -1cm]ff.south) (f3){Frontier$_N$};

@@

    \node[right](d) at ([xshift = 1.2cm,yshift = 0.7cm]c.east) {DSL $\mathcal{D}$};
    \node[right](t) at ([xshift = 1.2cm,yshift = -0.7cm]c.east) {Weights $\theta$};
    \draw [-> ] (c.east) -- (d.west);
    \draw [-> ] (c.east) -- (t.west);

### 2018-07-07 nips_2018.tex
first poster commit
poster acknowledgments

\parbox{0.58\textwidth}{

%\paragraph{Outlook.}
We contribute an algorithm, \systemEnding, that learns to program by
bootstrapping a DSL with new domain-specific primitives that the algorithm
itself discovers, together with a neural recognition model that learns how to
efficiently deploy the DSL on new tasks. We believe this integration of top-down
symbolic representations and bottom-up neural networks --- both of them learned
--- helps make program induction systems more generally useful for AI. Many
directions remain open.
%\paragraph{Future.}
Two immediate goals are to integrate more sophisticated neural recognition
models~\cite{devlin2017robustfill} and program
synthesizers~\cite{solar2008program}, which may improve performance in some
domains over the generic methods used here.
We are in the process of applying our algorithm to generative programs and
prototyped this with a turtle-like domain: Figure~\ref{geomCompiled} gives some
preliminary results for turtle graphics  --- see Section 1 of the supplementary material for more
details.  Another direction is to explore DSL meta-learning: can we find a
\emph{single} universal primitive set that could effectively bootstrap DSLs for
new domains, including the three domains considered,  but also many others?
}\hfill
\begin{minipage}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{figures/geomCompiled.eps} 
  \captionof{figure}{
  Top left: Example training tasks. Top right: samples from the learned DSL.
 Bottom: \% holdout testing tasks solved (middle), on sides are the averaged samples from the DSL
  before any training (left) and after last iteration (right).}
\label{geomCompiled}
\end{minipage}

>>>>

%\parbox{0.58\textwidth}{

%\paragraph{Outlook.}
We contribute an algorithm, \systemEnding, that learns to program by
bootstrapping a DSL with new domain-specific primitives that the algorithm
itself discovers, together with a neural recognition model that learns how to
efficiently deploy the DSL on new tasks. We believe this integration of top-down
symbolic representations and bottom-up neural networks --- both of them learned
--- helps make program induction systems more generally useful for AI. Many
directions remain open.
%\paragraph{Future.}
Two immediate goals are to integrate more sophisticated neural recognition
models~\cite{devlin2017robustfill} and program
synthesizers~\cite{solar2008program}, which may improve performance in some
domains over the generic methods used here.
%% We are in the process of applying our algorithm to generative programs and
%% prototyped this with a turtle-like domain: Figure~\ref{geomCompiled} gives some
%% preliminary results for turtle graphics  --- see Section 1 of the supplementary material for more
%% details.
Another direction is to explore DSL meta-learning: can we find a
\emph{single} universal primitive set that could effectively bootstrap DSLs for
new domains, including the three domains considered,  but also many others?
%% }\hfill
%% \begin{minipage}{0.4\textwidth}
%%   \centering
%%   \includegraphics[width=\textwidth]{figures/geomCompiled.eps} 
%%   \captionof{figure}{
%%   Top left: Example training tasks. Top right: samples from the learned DSL.
%%  Bottom: \% holdout testing tasks solved (middle), on sides are the averaged samples from the DSL
%%   before any training (left) and after last iteration (right).}
%% \label{geomCompiled}
%% \end{minipage}
